---
title: "IEW12 Presentation Graphs"
author: "A H Sparks and E M Del Ponte"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{IEW12_slides}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(hrbrthemes)
library(dplyr)
library(ggplot2)
library(gsheet)
library(magrittr)
library(tidyr)
```

# Import article evaluations

```{r}
rrpp <- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
)
```

## Unnest the software that were used

```{r}
rrpp <- 
  rrpp %>%
  unnest(software_used = strsplit(software_used, ", "))
```

# Visualise evaluations

## Article classes

```{r}
ggplot(rrpp, aes(x = art_class)) +
  geom_bar(stat = "count",
           fill = "#0B5394",
           colour = "#0B5394") +
  xlab("Class(es)") +
  theme(axis.text.x = element_text(angle = 45,
                                   hjust = 1)) +
  ggtitle("Article Classification") +
  theme_ipsum_rc()
```

## Computational methods available

Are analysis scripts and any special software used available for inspection and
reuse to reproduce the work? Readily available (3) to not mentioned (1).

```{r}
ggplot(rrpp, aes(x = comp_mthds_avail)) +
  geom_bar(stat = "count",
           fill = "#0B5394",
           colour = "#0B5394") +
  ggtitle("Computational Methods Availability") +
  xlab("Score") +
  theme_ipsum_rc()
```

## Software availability

Is the software readily available? Open source (3, good) to proprietary and \$$
(1).

```{r}
ggplot(rrpp, aes(x = software_avail)) +
  geom_bar(stat = "count",
           fill = "#0B5394",
           colour = "#0B5394") +
  ggtitle("Software availability") +
  xlab("Score") +
  theme_ipsum_rc()
```

## Data availability

Is the data readily available from a proper archiving repository, e.g. Zenodo
or Dataverse (3) to not mentioned (1).

```{r}
ggplot(rrpp, aes(x = data_avail)) +
  geom_bar(stat = "count",
           fill = "#0B5394",
           colour = "#0B5394") +
  ggtitle("Data Availability") +
  xlab("Score") +
  theme_ipsum_rc()
```

## Software citations

Was the software used properly cited? All versions and packages cited (3) to
not described what was used (1).

```{r}
ggplot(rrpp, aes(x = software_cite)) +
  geom_bar(stat = "count",
           fill = "#0B5394",
           colour = "#0B5394") +
  ggtitle("Software Cited") +
  xlab("Score") +
  theme_ipsum_rc()
```

## Software used (cited)

What are the 10 most popular software packages used?

```{r}
tab <- table(rrpp$software_used)
tab_s <- sort(tab)
top10 <- tail(names(tab_s), 17) # checking the table, there are several ties
top_software <- subset(rrpp, software_used %in% top10)
top_software$software_used <- factor(top_software$software_used,
                                     levels = rev(top10))


ggplot(top_software, aes(x = software_used)) +
  geom_bar(stat = "count",
           fill = "#0B5394",
           colour = "#0B5394") +
  ggtitle("Top 10 Software Used") +
  xlab("Software") +
  ylab("Count") +
  theme_ipsum_rc() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
  

## Reproducibility score

Using the four areas above, computational method availability, software availability, software citations and data availability, how reproducible is the
paper? In the reproducibility score, the software availability and software
citation are weighted to half the value of data and computational method
availability.

### Calculate reproducibility score
```{r}
rrpp <-
  rrpp %>%
  rowwise() %>% 
  mutate(
    reproducibility_score =
      sum(comp_mthds_avail,
          (software_avail + software_cite) * 0.5,
          data_avail,
          na.rm = TRUE)
  )
```

### Graph reproducibility score

```{r}  
  ggplot(rrpp, aes(x = reproducibility_score)) +
  geom_bar(stat = "count",
           fill = "#0B5394",
           colour = "#0B5394") +
  ggtitle("Combined Reproducibility Score") +
  xlab("Score") +
  theme_ipsum_rc()
```

## Article class effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = art_class)) +
  geom_boxplot(outlier.shape = NA,
               colour = "#0B5394",
               fill = "#0B5394",
               alpha = 0.5) +
  geom_jitter(width = 0.15,
              alpha = 0.3,
              colour = "#0B5394") +
  ggtitle("Article Class Effect on Reproducibility") +
  xlab("Class(es)") +
  ylab("Score") +
  theme_ipsum_rc()
```

## Journal effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = abbreviation)) +
  geom_boxplot(outlier.shape = NA,
               colour = "#0B5394",
               fill = "#0B5394",
               alpha = 0.5) +
  geom_jitter(width = 0.15,
              alpha = 0.3,
              colour = "#0B5394") +
  ggtitle("Journal Effect on Reproducibility") +
  xlab("Journal") +
  ylab("Score") +
  theme_ipsum_rc() +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.5))
```

## Evaluator effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = assignee)) +
  geom_boxplot(outlier.shape = NA,
               colour = "#0B5394",
               fill = "#0B5394",
               alpha = 0.5) +
  geom_jitter(width = 0.15,
              alpha = 0.3,
              colour = "#0B5394") +
  ggtitle("Evaluator Effect on Reproducibility Score") +
  xlab("Evaluator") +
  ylab("Score") +
  theme_ipsum_rc()
```

## Five year impact factor effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(round(IF_5year, 1)))) +
  geom_boxplot(outlier.shape = NA,
               colour = "#0B5394",
               fill = "#0B5394",
               alpha = 0.5) +
  ggtitle("Five Year IF Effect on Reproducibility Score") +
  xlab("Impact Factor") +
  ylab("Score") +
  theme_ipsum_rc()
```

## Journal open access effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = open)) +
  geom_boxplot(outlier.shape = NA,
               colour = "#0B5394",
               fill = "#0B5394",
               alpha = 0.5) +
  geom_jitter(width = 0.15,
              alpha = 0.3,
              colour = "#0B5394") +
  ggtitle("Open Access Effect on Reproducibility Score") +
  xlab("Impact Factor") +
  ylab("Score") +
  theme_ipsum_rc()
```

## Journal reproducibility instructions effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(repro_inst))) +
  geom_boxplot(outlier.shape = NA,
               colour = "#0B5394",
               fill = "#0B5394",
               alpha = 0.5) +
  geom_jitter(width = 0.15,
              alpha = 0.3,
              colour = "#0B5394") +
  ggtitle("Reproducibility Instructions Effect on Reproducibility Score") +
  xlab("Reproducibility Instructions Score") +
  ylab("Score") +
  theme_ipsum_rc()
```
