---
title: "Sparks ANU Graphs for Open Science Presentation"
author: "Adam H Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sparks ANU Graphs for Open Science Presentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.width = 10, 
fig.height = 5,
fig.path = 'figures/',
dev = c('png')
)

library(dplyr)
library(ggplot2)
library(ggthemes)
library(hrbrthemes)
library(magrittr)
library(tidyr)

"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

# geom_flat_violin() code

geom_flat_violin <-
  function(mapping = NULL,
           data = NULL,
           stat = "ydensity",
           position = "dodge",
           trim = TRUE,
           scale = "area",
           show.legend = NA,
           inherit.aes = TRUE,
           ...) {
    layer(
      data = data,
      mapping = mapping,
      stat = stat,
      geom = GeomFlatViolin,
      position = position,
      show.legend = show.legend,
      inherit.aes = inherit.aes,
      params = list(trim = trim,
                    scale = scale,
                    ...)
    )
  }

#' @rdname ggplot2-ggproto
#' @format NULL
#' @usage NULL
#' @export
GeomFlatViolin <-
  ggproto(
    "GeomFlatViolin",
    Geom,
    setup_data = function(data, params) {
      data$width <- data$width %||%
        params$width %||% (resolution(data$x, FALSE) * 0.9)
      
      # ymin, ymax, xmin, and xmax define the bounding rectangle for each group
      data %>%
        group_by(group) %>%
        mutate(
          ymin = min(y),
          ymax = max(y),
          xmin = x,
          xmax = x + width / 2
        )
    },
    
    draw_group = function(data, panel_scales, coord) {
      # Find the points for the line to go all the way around
      data <- transform(data,
                        xminv = x,
                        xmaxv = x + violinwidth * (xmax - x))
      
      # Make sure it's sorted properly to draw the outline
      newdata <- rbind(plyr::arrange(transform(data, x = xminv), y),
                       plyr::arrange(transform(data, x = xmaxv), -y))
      
      # Close the polygon: set first and last point the same
      # Needed for coord_polar and such
      newdata <- rbind(newdata, newdata[1, ])
      
      ggplot2:::ggname("geom_flat_violin",
                       GeomPolygon$draw_panel(newdata, panel_scales, coord))
    },
    
    draw_key = draw_key_polygon,
    
    default_aes = aes(
      weight = 1,
      colour = "grey20",
      fill = "white",
      size = 0.5,
      alpha = NA,
      linetype = "solid"
    ),
    
    required_aes = c("x", "y")
  )
```

# Import article evaluations

```{r import}
rrpp <- gsheet::gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
)
```

## Calculate reproducibility score

```{r calculate-score}
rrpp <-
  rrpp %>%
  mutate(
    reproducibility_score =
      if_else(
        condition = data_avail > 0,
        
        true = as.integer(comp_mthds_avail) +
          as.integer(software_avail) +
          as.integer(software_cite) +
          as.integer(data_avail),
        
        false = as.integer(data_avail),
        
        missing = as.integer(0)
      )
  )
```

## Unnest the software that were used

Create a tidy data frame of the data by unnesting software used as in many cases
multiple software packages were used, so will end up with multiple rows for same
article, one for each software.

```{r unnest-software}
rrpp_software <- 
  rrpp %>%
  unnest(software_used = strsplit(software_used, ", "))
```

# Visualise evaluations

## Article classes

```{r article-classes}
ggplot(rrpp, aes(x = art_class)) +
  geom_bar(stat = "count",
           aes(fill = art_class)) +
  xlab("Class(es)") +
  scale_fill_few() +
  ggtitle("Article Classification") +
  coord_flip() +
  theme_ipsum_rc() +
  guides(fill = FALSE)
```

## Journals and articles sampled

```{r journals-sampled}
ggplot(rrpp, aes(x = abbreviation)) +
  geom_bar(stat = "count",
           aes(fill = art_class)) +
  xlab("Journal Abbreviation") +
  scale_fill_few(name = "Article Class") +
  ggtitle("Journals Sampled") +
  coord_flip() +
  theme_ipsum_rc()
```

## Computational methods available

```{r comp-methods}
ggplot(rrpp, aes(x = comp_mthds_avail)) +
  geom_bar(aes(fill = art_class)) +
  ggtitle("Computational Methods Availability") +
  xlab("Score") +
  scale_fill_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc()
```

## Software availability

Was the software used readily available and preferably open-source?

```{r software-avail}
ggplot(rrpp, aes(x = software_avail)) +
  geom_bar(aes(fill = art_class)) +
  ggtitle("Software Availability") +
  xlab("Score") +
  scale_fill_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc()
```

## Data availability

Was the data made available?

```{r data-avail}
ggplot(rrpp, aes(x = data_avail)) +
  geom_bar(aes(fill = art_class)) +
  ggtitle("Data Availability") +
  xlab("Score") +
  scale_fill_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc()
```

## Software citations

Was the software that was used properly cited?

```{r software-cite}
ggplot(rrpp, aes(x = software_cite)) +
  geom_bar(aes(fill = art_class)) +
  ggtitle("Software Cited") +
  xlab("Score") +
  scale_fill_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc()
```

## Software used (cited)

Count and sort top 10 software packages cited. There are likely others that are
used, but they have not been properly identified by the authors.

```{r software-used}
tab <- table(rrpp_software$software_used)
tab_s <- sort(tab)
top10 <- tail(names(tab_s), 17) # checking the table, there are several ties
top_software <- subset(rrpp_software, software_used %in% top10)
top_software$software_used <- factor(top_software$software_used,
                                     levels = rev(top10))

ggplot(top_software, aes(x = software_used)) +
  geom_bar(aes(fill = art_class)) +
  ggtitle("Top 10 Software Used") +
  xlab("Software") +
  ylab("Count") +
  scale_fill_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc()
```

## Reproducibility score

The reproducibility score was calculated as the sum of the scores for computational
method availability, 

```{r reproducibility-score}
ggplot(rrpp, aes(x = reproducibility_score)) +
  geom_bar(aes(fill = art_class)) +
  ggtitle("Combined Reproducibility Score") +
  xlab("Score") +
  scale_fill_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc()
```

## Article class effect on reproducibility score

```{r art-class-repro-score}
ggplot(rrpp,
       aes(
         fill = art_class,
         colour = art_class,
         x = art_class,
         y = reproducibility_score
       )) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0)) +
  geom_jitter(width = .15,
              size = .5) +
  geom_boxplot(width = 0.1,
               outlier.shape = NA,
               color = "#666666") +
  ggtitle("Article Class Effect on Reproducibility") +
  xlab("Class(es)") +
  ylab("Score") +
  scale_fill_few(name = "Article Class") +
  scale_colour_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc() +
  guides(fill = FALSE, colour = FALSE)
```

## Journal effect on reproducibility score

```{r journal-repro-score}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = abbreviation)) +
  geom_boxplot(fill = "#5da5da",
               colour = "#666666") +
  ggtitle("Journal Effect on Reproducibility") +
  xlab("Journal") +
  ylab("Score") +
  scale_fill_few(name = "Article Class") +
  scale_colour_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc() +
  guides(fill = FALSE, colour = FALSE)
```

## Evaluator effect on reproducibility score

```{r eval-repro-score}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = assignee)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0),
                   colour = "#5da5da",
                   fill = "#5da5da") +
  geom_jitter(
    width = .15,
    size = .5,
    colour = "#5da5da",
    fill = "#5da5da"
  ) +
  geom_boxplot(width = 0.1,
               outlier.shape = NA,
               color = "#666666") +
  ggtitle("Evaluator Effect on Reproducibility Score") +
  xlab("Evaluator") +
  ylab("Score") +
  scale_fill_few(name = "Article Class") +
  scale_colour_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc() +
  guides(fill = FALSE, colour = FALSE)
```

## Five year impact factor effect on reproducibility score

```{r 5-year-repro-score}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(round(IF_5year, 1)))) +
  geom_boxplot(fill = "#5da5da",
               colour = "#666666") +
  ggtitle("Five Year IF Effect on Reproducibility Score") +
  xlab("Impact Factor") +
  ylab("Score") +
  scale_fill_few(name = "Article Class") +
  scale_colour_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc() +
  guides(fill = FALSE, colour = FALSE)
```

## Journal open access effect on reproducibility score

```{r open-access-repro-score}
ggplot(rrpp,
       aes(
         y = reproducibility_score,
         x = open)) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    fill = "#5da5da",
    colour = "#5da5da"
  ) +
  geom_jitter(
    width = .15,
    size = .5,
    fill = "#5da5da",
    colour = "#5da5da"
  ) +
  geom_boxplot(width = 0.1,
               outlier.shape = NA,
               color = "#666666") +
  ggtitle("Open Access Effect on Reproducibility Score") +
  xlab("Impact Factor") +
  ylab("Score") +
  scale_fill_few(name = "Article Class") +
  scale_colour_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc() +
  guides(fill = FALSE, colour = FALSE)
```

## Journal reproducibility instructions effect on reproducibility score

```{r repro-instructions-repro-score}
ggplot(rrpp,
       aes(y = reproducibility_score,
           x = as.factor(repro_inst))) +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    fill = "#5da5da",
    colour = "#5da5da"
  ) +
  geom_jitter(
    width = .15,
    size = .5,
    fill = "#5da5da",
    colour = "#5da5da"
  ) +
  geom_boxplot(width = 0.1,
               outlier.shape = NA,
               color = "#666666") +
  ggtitle("Reproducibility Instructions Effect on Reproducibility Score") +
  xlab("Journal Reproducibility Instructions Score") +
  ylab("Article Score") +
  scale_fill_few(name = "Article Class") +
  scale_colour_few(name = "Article Class") +
  coord_flip() +
  theme_ipsum_rc() +
  guides(fill = FALSE, colour = FALSE)
```
